---
title: "Spatial asynchrony and cross-scale climate interactions in populations of a coldwater stream fish"
author: 
  - George P. Valentine, Dept. Fish, Wildlife, & Conservation Biology, Colorado State University, george.valentine@colostate.edu
  - Xinyi Lu, Dept. Fish, Wildlife, & Conservation Biology, Colorado State University
  - Evan S. Childress, Shenandoah National Park
  - C. Andrew Dolloff, U.S. Forest Service Southern Research Station
  - Nathaniel P. Hitt, U.S. Geological Survey Eastern Ecological Science Center
  - Matthew A. Kulp, Great Smoky Mountains National Park
  - Benjamin H. Letcher, U.S. Geological Survey Eastern Ecological Science Center
  - Kasey C. Pregler, Dept. of Env. Science, Policy, & Management, University of California Berkeley
  - Jacob M. Rash, North Carolina Wildlife Resources Commission
  - Mevin B. Hooten, Dept. Statistics & Data Sciences, The University of Texas at Austin
  - Yoichiro Kanno, Dept. Fish, Wildlife, & Conservation Biology, Colorado State University, yoichiro.kanno@colostate.edu
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: FALSE
    number_sections: TRUE
    keep_tex: true
geometry: "left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm"
fontsize: 11pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \pagenumbering{gobble}
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{bm}
  - \DeclareUnicodeCharacter{0008}{ }
  - \setlength{\parindent}{4em}
  - \usepackage{flafter}
linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
params:
  run_name: ["v2.0"]
---

```{r setup, include=FALSE}
# load required R packages
library(tidyverse)    # For tidy data management
library(here)         # For auto-locating files within the working directory
library(bookdown)     # For numbering figures, tables, and equations
library(stringr)      # For manipulating strings in figure captions
library(ncf)          # For creating correlograms in missing data simulation (Appendix 1)
library(ggplot2)      # For tidy plotting
library(cowplot)      # For creating gridded plots
library(gridGraphics) # For including base R plots in gridded plots
library(formatR)      # For displaying tidy code in output
library(knitr)        # For making tidy tables
library(forcats)      # For cats
library(latex2exp)    # For writing special characters in plot labels
library(MCMCvis)      # MCMC tools
library(kableExtra)   # For formatting tables
library(tinytex)

knitr::opts_chunk$set(echo = F,
                      tidy = T,
                      warning = F,
                      message = F,
                      tidy.opts=list(width.cutoff=50))

# Save the directory from which to pull results files
run_dir <- here::here("results", params$run_name)

# Load figures and tables to include
load(file = file.path(run_dir, "plots.rdata"))
load(file = file.path(run_dir, "tables.rdata"))
```

\newpage

# Abstract

```{r abstract, child = 'abstract.Rmd'}
```

\newpage
\pagenumbering{arabic}

# Introduction

```{r intro, child = 'introduction.Rmd'}
```

\newpage

# Methods

```{r methods, child = 'methods.Rmd'}
```

\newpage

# Results

```{r results, child = 'results.Rmd'}
```

\newpage

# Discussion

```{r discussion, child = 'discussion_ecology.Rmd'}
```

\newpage

# Acknowledgements
We thank the numerous agencies and organizations that provided the data utilized in this study. Without the hard work of numerous biologists, technicians, and volunteers, this study would not have been possible. This research was funded by Cooperative Agreement No. G21AC10205 from the U.S. Geological Survey Southeast Climate Adaptation Science Center, and Cooperative Agreement No. F20AC11372 from the U.S. Fish and Wildlife Service. The findings and conclusions in this report are those of the authors and do not necessarily represent the views of the U.S. Fish and Wildlife Service.

\newpage

# References

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage

# Appendix

```{r appendix, child = 'appendix.Rmd'}
```
