---
title: "Spatial asynchrony and cross-scale climate interactions in populations of a coldwater stream fish"
author: 
  - George P. Valentine^[Corresponding Author], Dept. Fish, Wildlife, & Conservation Biology
  - and Graduate Degree Program in Ecology, Colorado State University,
  - george.valentine@colostate.edu
  - Xinyi Lu, Dept. Fish, Wildlife, & Conservation Biology, Colorado State University
  - Evan S. Childress, Shenandoah National Park
  - C. Andrew Dolloff, U.S. Forest Service Southern Research Station
  - Nathaniel P. Hitt, U.S. Geological Survey Eastern Ecological Science Center
  - Matthew A. Kulp, Great Smoky Mountains National Park
  - Benjamin H. Letcher, U.S. Geological Survey Eastern Ecological Science Center
  - Kasey C. Pregler, Dept. of Env. Science, Policy, & Management, University of California Berkeley
  - Jacob M. Rash, North Carolina Wildlife Resources Commission
  - Mevin B. Hooten, Dept. Statistics & Data Sciences, The University of Texas at Austin
  - Yoichiro Kanno, Dept. Fish, Wildlife, & Conservation Biology
  - and Graduate Degree Program in Ecology, Colorado State University, 
  - yoichiro.kanno@colostate.edu
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: FALSE
    number_sections: TRUE
    keep_tex: true
geometry: "left = 2.5cm, right = 2cm, top = 2cm, bottom = 2cm"
fontsize: 11pt
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
  - \pagenumbering{gobble}
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{1.5}
  - \usepackage{bm}
  - \DeclareUnicodeCharacter{0008}{ }
  - \setlength{\parindent}{4em}
  - \usepackage{flafter}
linkcolor: blue
bibliography: bibliography.bib
csl: apa.csl
params:
  run_name: ["v4.0"]
---

```{r setup, include=FALSE}
# load required R packages
library(tidyverse)    # For tidy data management
library(here)         # For auto-locating files within the working directory
library(bookdown)     # For numbering figures, tables, and equations
library(stringr)      # For manipulating strings in figure captions
library(ncf)          # For creating correlograms in missing data simulation (Appendix 1)
library(ggplot2)      # For tidy plotting
library(cowplot)      # For creating gridded plots
library(gridGraphics) # For including base R plots in gridded plots
library(formatR)      # For displaying tidy code in output
library(knitr)        # For making tidy tables
library(forcats)      # For cats
library(latex2exp)    # For writing special characters in plot labels
library(MCMCvis)      # MCMC tools
library(kableExtra)   # For formatting tables
library(tinytex)

knitr::opts_chunk$set(echo = F,
                      tidy = T,
                      warning = F,
                      message = F,
                      tidy.opts=list(width.cutoff=50))

options(scipen=999) # turns off the use of scientific notation

# Save the directory from which to pull results files
run_dir <- here::here("results", params$run_name)

# Load figures and tables to include
load(file = file.path(run_dir, "plots.rdata"))
load(file = file.path(run_dir, "tables.rdata"))
```

\newpage

# Abstract {-}

```{r abstract, child = 'abstract.Rmd'}
```

\vfill

\noindent Keywords: Bayesian, brook trout, climate, Portfolio Effect, stream fish, synchrony, weather

\vfill

\newpage
\pagenumbering{arabic}

# Introduction

```{r intro, child = 'introduction.Rmd'}
```

\newpage

# Methods

```{r methods, child = 'methods.Rmd'}
```

\newpage

# Results

```{r results, child = 'results.Rmd'}
```

\newpage

# Discussion

```{r discussion, child = 'discussion_ecology.Rmd'}
```

\newpage

# Acknowledgements
We thank the numerous agencies and organizations that provided the data utilized in this study. This research was funded by Cooperative Agreement No. G21AC10205 from the U.S. Geological Survey Southeast Climate Adaptation Science Center, and Cooperative Agreement No. F20AC11372 from the U.S. Fish and Wildlife Service. The findings and conclusions in this report are those of the authors and do not necessarily represent the views of the U.S. Fish and Wildlife Service. Any use of trade, product, or firm names is for descriptive purposes only and does not imply endorsement by the U.S. Government.

# Conflict of interest statement
The authors have no conflicts of interest to declare.

# Data Availability
Data are archived at sciencebase.gov with DOI 10.5066/P9DQID6G.

\newpage

# References

```{r biblio, child = 'bibliography.Rmd'}
```

\newpage

\begin{center}

SPATIAL ASYNCHRONY AND CROSS-SCALE CLIMATE INTERACTIONS IN POPULATIONS OF A COLDWATER STREAM FISH

George P. Valentine, Dept. Fish, Wildlife, and Conservation Biology and Graduate Degree Program in Ecology, Colorado State University\\
Xinyi Lu, Dept. Fish, Wildlife, and Conservation Biology, Colorado State University\\
Evan S. Childress, Shenandoah National Park\\
C. Andrew Dolloff, U.S. Forest Service Southern Research Station\\
Nathaniel P. Hitt, U.S. Geological Survey Eastern Ecological Science Center\\
Matthew A. Kulp, Great Smoky Mountains National Park\\
Benjamin H. Letcher, U.S. Geological Survey Eastern Ecological Science Center\\
Kasey C. Pregler, Dept. of Env. Science, Policy, and Management, University of California Berkeley\\
Jacob M. Rash, North Carolina Wildlife Resources Commission\\
Mevin B. Hooten, Dept. Statistics and Data Sciences, The University of Texas at Austin\\
Yoichiro Kanno, Dept. Fish, Wildlife, and Conservation Biology and Graduate Degree Program in Ecology, Colorado State University

Any use of trade, product, or firm names is for descriptive purposes only and does not imply endorsement by the U.S. Government.

\end{center}

# Appendix

```{r appendix, child = 'appendix.Rmd'}
```
