---
title: ''
output: bookdown::pdf_document2
date: "`r Sys.Date()`"
---

## Correlogram Analysis
The average scale and magnitude of spatial synchrony in both YOY and adult brook trout was relatively low compared with those of a suite of climate variables (Fig. \@ref(fig:compound-corrgram-plot)). Correlation lengths in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$quantiles["0.025", "x"], 2)` km and `r round(Adult_corrgram_summary.table$quantiles["0.025", "x"], 2)` km, respectively. Summer air and water temperature and winter streamflow and precipitation were significantly synchronous to scales of 400km or more. Average pairwise correlations in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$Regional.synch[1], 3)` and `r round(Adult_corrgram_summary.table$Regional.synch[1], 3)`, respectively, while those of the climate variables ranged from `r round(SummWaterTempObs_corrgram_summary.table$Regional.synch[1], 3)` up to `r round(FlowEst_corrgram_summary.table$Regional.synch[1], 3)`. Initial pairwise correlation was higher in the northern subregion for both life stages, which in turn caused the average correlation in log density in northern populations to be slightly higher than southern ones. However, neither the scale nor magnitude of synchrony differed significantly between subregions (Fig. \@ref(fig:compound-corrgram-BKT-plot)).

```{r compound-corrgram-plot, fig.cap="Spline correlogram of pairwise correlation in brook trout (BKT) log density and selected climate variables for the southeast USA. Climate variables: mean estimated monthly winter flow, mean daily observed summer air temperature, mean daily observed summer water temperature, total observed monthly winter precipitation. Brook trout density is log transformed. Shading indicates 95% confidence intervals. Dotted lines represent average correlation. Climate data sources: USGS NHDPlus v2.1, US Forest Service, NOAA."}
compound_corrgram2.plot
```

```{r compound-corrgram-BKT-plot, fig.cap="Spline correlogram of log brook trout density by life stage and subregion."}
compound_corrgram_BKT.plot
```

## Hierarchical Model
Lacking random effects, predictive ability of the climate effect-only models was modest. Bayesian p-values for mean and coefficient of variation of pass 1 YOY abundance were `r round(PPC_pvals.table[1,4], 2)` and `r round(PPC_pvals.table[2,4], 2)`. Predictive ability of the random effects models was considerably better. Bayesian p-values for mean and coefficient of variation of pass 1 YOY abundance were `r round(PPC_pvals.table[3,4], 2)` and `r round(PPC_pvals.table[4,4], 2)`.

Electrofishing capture probability was higher for adults than YOY. Estimates of capture probability by agency varied from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` for YOY brook trout and from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` for adult brook trout (Fig. \@ref(fig:detect-probs)).

### Regional and Subregional Climate Effects
Climate effects on brook trout abundance varied by subregion and life stage, as represented by posterior distributions of the mean parameters for $\bf{\beta}_i$ (Fig. \@ref(fig:cov-effects-plot)). In all cases, YOY were more affected by climate than were adults. At the regional scale, all three environmental covariates had negative effects on YOY abundance, while they had little effect on adult abundance. Winter high flow had the strongest negative effect on YOY abundance, followed by spring high flow and high temperatures in the previous summer.

```{r cov-effects-plot, fig.cap = "Covariate effects on brook trout log density by age class and subregion. Covariates: mean 0.9Q summer air temperature (year t-1), max 0.9Q winter flow (year t), max 0.9Q spring flow (year t)."}
cov_effects.plot
```

Covariate effects at the subregional scale varied. As hypothesized, air temperature had a stronger effect on YOY in the south than in the north. Within the northern subregion, YOY abundance was exclusively driven by flow, with no effect of summer air temperature. Within the southern subregion, summer air temperature and winter flow were had the strongest negative effect on YOY abundance. The effect of spring flow on YOY in the south trended positive. A slight overall negative effect of summer air temperature on adult abundance was driven by the response of northern populations. Uncertainty in climate effects on adults in southern populations was much greater than that of northern populations.

### Local Climate Effects
Climate effects varied considerably between stream segments (Fig. \@ref(fig:YOY-climate-effects-map)). Some experienced positive effects, while others experienced negative effects.  There was slight geographic correlation in climate effects: the effect of summer temperature was positively correlated with latitude, and the effects of all three climate variables were correlated with elevation (Fig. \@ref(fig:YOY-betas-corrPlot-plot)). Furthermore, strong flow responses were generally correlated with segments that experience high winter and spring flows, as predicted by the NHDplus [@USGS2016]. There was no notable spatial structure in covariate effects on YOY brook trout abundance (model $\bf{\beta}_i$s) (Fig. \@ref(fig:YOY-climate-effects-semivariogram-plot)).

### Synchrony
Estimates of segment-specific ICC values varied from `r round(min(YOY_ICCs.table$mean), 2)` to `r round(max(YOY_ICCs.table$mean), 2)` for YOY brook trout and from `r round(min(Adult_ICCs.table$mean), 2)` to `r round(max(Adult_ICCs.table$mean), 2)` for adult brook trout. YOY brook trout showed higher average synchrony than adult brook trout (`r round(mean(YOY_ICCs.table$mean), 2)` vs. `r round(mean(Adult_ICCs.table$mean), 2)`). On average, northern brook trout populations were more synchronous than southern populations (average YOY ICC: `r round(mean(YOY_ICCs_N.table[,"mean"]), 2)` vs. `r round(mean(YOY_ICCs_S.table[,"mean"]), 2)`). A visual inspection revealed that several of the least snchronous populations were located in heavily forested hills at mid- to high-elevation. Several of the most synchronous populations (highest YOY ICC) were in northeast Maryland at low-elevation sites near Chesapeake Bay (Fig.\@ref(fig:YOY-ICC-map)). There was considerable geographic heterogeneity in spatial synchrony (Fig.\@ref(fig:YOY-ICC-map)), and segment-specific synchrony showed moderate spatial structure (Fig. \@ref(fig:YOY-ICC-semivariogram-plot)), lending support to the idea that populations nearer to each other are more similar than populations farther from each other. 

```{r YOY-ICC-map, fig.cap = "Intraclass correlation coefficient (ICC) values for populations of young-of-year brook trout in the southeastern USA."}
YOY_ICC_map.plot
```

### Climate Effects on Synchrony   
The range of climate effects on brook trout populations varied by age class, but not by climate variable. YOY experienced a wider range of responses to climate than did adults (Fig. \@ref(fig:climate-ranges-plot)). However, there were not significant differences in the ranges of climate effects. 

```{r climate-ranges-plot, fig.cap = "Range of mean segment-specific climate effects by life stage."}
climate_effect_ranges.plot
```
