---
title: ''
output: bookdown::pdf_document2
date: "`r Sys.Date()`"
---

## Correlogram Analysis

The average scale and magnitude of spatial synchrony in both YOY and adult brook trout was relatively low compared with those of a suite of climate variables (Fig. \@ref(fig:compound-corrgram-plot)). Correlation lengths measured using the 95% confidence envelope of the spline correlogram were `r round(YOY_corrgram_summary.table$quantiles["0.025", "x"])` km in YOY and `r round(Adult_corrgram_summary.table$quantiles["0.025", "x"])` km in adult brook trout. Point estimates for the scale of synchrony were roughly 150 km for both life stages. Summer air and water temperature and winter streamflow and precipitation were significantly synchronous to scales of 400km or more. Average pairwise correlations in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$Regional.synch[1], 2)` and `r round(Adult_corrgram_summary.table$Regional.synch[1], 2)`, respectively, while those of the climate variables ranged from `r round(SummWaterTempObs_corrgram_summary.table$Regional.synch[1], 2)` to `r round(FlowEst_corrgram_summary.table$Regional.synch[1], 2)`. Initial pairwise correlation was considerably higher in the northern subregion for both life stages. However, neither the scale nor average magnitude of synchrony differed between subregions (Fig. \@ref(fig:faceted-corrgram-plot)).

```{r compound-corrgram-plot, fig.cap="Spline correlogram of pairwise correlation in brook trout (BKT) log density and selected climate variables for the southeast USA. Climate variables: mean estimated monthly winter flow, mean daily observed summer air temperature, mean daily observed summer water temperature, total observed monthly winter precipitation. Brook trout density is log transformed. Shading indicates 95% confidence intervals. Dotted lines represent average correlation. Climate data sources: USGS NHDPlus v2.1, US Forest Service, NOAA."}
compound_corrgram2.plot
```

```{r faceted-corrgram-plot, fig.cap="Spline correlogram of log brook trout density by life stage and subregion. Shaded regions represent 95% confidence envelope. Dotted lines represent average correlation."}
compound_corrgram_BKT.plot
```

## Hierarchical Model

Lacking random effects, predictive ability of the climate effect-only models was modest. Bayesian p-values for mean and coefficient of variation of pass 1 YOY abundance were `r round(PPC_pvals.table[1,4], 2)` and `r round(PPC_pvals.table[2,4], 2)`. Predictive ability of the random effects models was considerably better. Bayesian p-values for mean and coefficient of variation of pass 1 YOY abundance were `r round(PPC_pvals.table[3,4], 2)` and `r round(PPC_pvals.table[4,4], 2)`. Electrofishing capture probability was higher for adults than YOY. Estimates of capture probability by agency varied from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` for YOY and from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` for adults (Fig. \@ref(fig:detect-probs)).

### Regional and Subregional Climate Effect

Climate effects on brook trout abundance varied by subregion and life stage, as represented by posterior distributions of the mean parameters for $\bm{\mu}_\beta$ (Fig. \@ref(fig:cov-effects-plot)). In all cases, YOY were more affected by climate than were adults. At the regional scale, all three environmental covariates had negative effects on YOY abundance, while they had little effect on adult abundance. Winter high flow had the strongest negative effect on YOY abundance, followed by spring high flow and high temperatures in the previous summer.

```{r cov-effects-plot, fig.cap = "Posterior distributions for climate effects on brook trout log density by life stage and subregion. Climate variables: average 0.9Q summer air temperature (year t-1), max 0.9Q winter stream flow (year t), max 0.9Q spring stream flow (year t)."}
cov_effects.plot
```

Covariate effects at the subregional scale varied. As hypothesized, air temperature had a stronger effect on YOY in the south than in the north. Within the northern subregion, YOY abundance was exclusively driven by flow, with no effect of summer air temperature. Within the southern subregion, summer air temperature and winter flow were had the strongest negative effect on YOY abundance. The effect of spring flow on YOY in the south trended positive. A slight overall negative effect of summer air temperature on adult abundance was driven by the response of northern populations. Uncertainty in climate effects on adults in southern populations was much greater than that of northern populations.

### Local Climate Effects

Climate effects varied considerably among stream segments (Fig. \@ref(fig:YOY-climate-effects-map)). Some experienced positive effects, while others experienced negative effects. The range of local effects for winter stream flow on YOY (`r round(cov_effect_ranges.table[2,"mean_range"], 1)`) was somewhat narrower than that of spring stream flow (`r round(cov_effect_ranges.table[3,"mean_range"], 1)`) or summer temperature (`r round(cov_effect_ranges.table[1,"mean_range"], 1)`, Fig. \@ref(fig:YOY-climate-effects-map)). YOY experienced a slightly broader average range of climate effects than adults (`r round(mean(cov_effect_ranges.table[1:3,"mean_range"]), 1)` vs. `r round(mean(cov_effect_ranges.table[4:6,"mean_range"]), 1)`). Visual inspection and correlation analysis demonstrated that there was little influence of local habitat on model $\bm{\beta}_i$s (Table \@ref(tab:YOY-betas-corr-table)). There was no notable spatial structure in covariate effects on YOY brook trout abundance (model $\bm{\beta}_i$s) (Fig. \@ref(fig:YOY-climate-effects-semivariogram-plot)).

```{r YOY-climate-effects-map, fig.cap="Local climate effects on brook trout young-of-year abundance (model $\\bm{\\beta}_i$s). a) average 0.9Q summer air temperature (year t-1), b) max 0.9Q winter stream flow (year t), and c) max 0.9Q spring stream flow (year t).", fig.height = 8}
plot_grid(YOY_SummTemp_betas.plot,
             YOY_WintFlow_betas.plot,
             YOY_SprFlow_betas.plot,
          labels = c("a)", "b)", "c)"),
          label_size = 11,
          nrow = 3)
```


### Synchrony

Estimates of segment-specific ICC values varied from `r round(min(YOY_ICCs.table$mean), 2)` to `r round(max(YOY_ICCs.table$mean), 2)` for YOY brook trout and from `r round(min(Adult_ICCs.table$mean), 2)` to `r round(max(Adult_ICCs.table$mean), 2)` for adult brook trout. YOY brook trout showed higher average synchrony than adult brook trout (`r round(mean(YOY_ICCs.table$mean), 2)` vs. `r round(mean(Adult_ICCs.table$mean), 2)`). On average, northern brook trout populations were more synchronous than southern populations (average YOY ICC: `r round(mean(YOY_ICCs_N.table[,"mean"]), 2)` vs. `r round(mean(YOY_ICCs_S.table[,"mean"]), 2)`). There was little correlation between ICC and and local habitat (Table \@ref(tab:YOY-ICCs-corr-table)). Several of the most synchronous populations (highest YOY ICC) were in northeast of the study region (Fig. \@ref(fig:YOY-ICC-map)). There was considerable geographic heterogeneity in spatial synchrony (Fig.\@ref(fig:YOY-ICC-map)), and segment-specific synchrony showed moderate spatial structure (Fig. \@ref(fig:YOY-ICC-semivariogram-plot)), lending support to the idea that populations nearer to each other are more similar than populations farther from each other. 

```{r YOY-ICC-map, fig.cap = "Intraclass correlation coefficient (ICC) values for populations of young-of-year brook trout in the southeastern USA. High ICC values indicate synchrony, while low ICC values indicate asynchrony."}
YOY_ICC_map.plot
```