---
title: ''
output: bookdown::pdf_document2
date: "`r Sys.Date()`"
---

## Correlogram Analysis
The average scale and magnitude of spatial synchrony in both YOY and adult brook trout was relatively low compared with those of a suite of climate variables (Fig. \@ref(fig:compound-corrgram-plot)). Correlation lengths in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$quantiles["0.025", "x"], 2)` km and `r round(Adult_corrgram_summary.table$quantiles["0.025", "x"], 2)` km, respectively. Summer air and water temperature and winter streamflow and precipitation were significantly synchronous to scales of 400km or more. Average pairwise correlations in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$Regional.synch[1], 3)` and `r round(Adult_corrgram_summary.table$Regional.synch[1], 3)`, respectively, while those of the climate variables ranged from `r round(SummWaterTempObs_corrgram_summary.table$Regional.synch[1], 3)` up to `r round(FlowEst_corrgram_summary.table$Regional.synch[1], 3)`. Initial pairwise correlation was higher in the northern subregion for both life stages, which in turn caused the average correlation in log density in northern populations to be slightly higher than southern ones. However, neither the scale nor magnitude of synchrony differed significantly between subregions (Fig. \@ref(fig:compound-corrgram-BKT-plot)).

```{r compound-corrgram-plot, fig.cap="Spline correlogram of pairwise correlation in brook trout (BKT) log density and selected climate variables for the southeast USA. Climate variables: mean estimated monthly winter flow, mean daily observed summer air temperature, mean daily observed summer water temperature, total observed monthly winter precipitation. Brook trout density is log transformed. Shading indicates 95% confidence intervals. Dotted lines represent average correlation. Climate data sources: USGS NHDPlus v2.1, US Forest Service, NOAA."}
compound_corrgram2.plot
```

```{r compound-corrgram-BKT-plot, fig.cap="Spline correlogram of log brook trout density by life stage and subregion."}
compound_corrgram_BKT.plot
```

## Hierarchical Model
Posterior predictive checks suggest little evidence of lack of fit between model estimates and data. Bayesian p-values for mean and coefficient of variation of pass 1 abundance in the full model for YOY were between `r round(min(PPC_pvals.table$mean), 3)` and `r round(max(PPC_pvals.table$mean), 3)`. Electrofishing capture probability was higher for adults than YOY. Estimates of capture probability by agency varied from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 3)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 3)` for YOY brook trout and from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 3)` to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 3)` for adult brook trout (Fig. \@ref(fig:detect-probs)).

### Regional and Subregional Climate Effects
Climate effects on brook trout abundance varied by subregion and life stage, as represented by posterior distributions of the mean parameters for $\bf{\beta}_i$ (Fig. \@ref(fig:cov-effects)). In all cases, YOY were more affected by climate than were adults. At the regional scale, all three environmental covariates had significant negative effects on log density of YOY, while they had nonsignificant effects on log density of adults. Average 90th percentile summer temperature in the preceding year had the strongest negative effect on YOY abundance, followed by maximum 90th percentile winter flow and maximum 90th percentile spring flow. Summer temperature was the only climate variable who's effect varied significantly by region: the effect was strong in the southern subregion, but negligible in the northern subregion. Covariate effects on log density of YOY at the subregional scale, however, varied. Within the northern subregion, winter flow had the only significant negative effect on log density of YOY, and the mean effect of summer air temperature was in fact positive. Spring flow had no effect on log density of YOY in this subregion. Within the southern subregion, average 90th percentile summer temperature in the preceding year had a strong negative effect on log YOY density, and the effect of winter flow was also negative. Spring flow had a mild positive effect in this subregion. 

```{r cov-effects, fig.cap = "Covariate effects on brook trout log density by age class and subregion. Covariates: mean 0.9Q summer air temperature (year t-1), max 0.9Q winter flow (year t), max 0.9Q spring flow (year t)."}
cov_effects.plot
```

### Local Climate Effects
Climate effects varied moderately between stream segments. Local climate effects were again stronger for the YOY life stage than the adult life stage, and they were again stronger for summer temperature than winter flow (Fig. \@ref(fig:YOY-climate-effects-map)). Here, we report values for the YOY model. The range of local effects for summer temperature was slightly larger than the range of local effects for winter flow. Using the regional model, estimates of segment-specific effects (model $\bf{\beta}_i$s) for summer temperature ranged from `r round(cov_effect_ranges.table[1, "min_mean"], 3)` (`r round(cov_effect_ranges.table[1, "min_95HDPL"], 3)`, `r round(cov_effect_ranges.table[1, "min_95HDPU"], 3)`) to `r round(cov_effect_ranges.table[1, "max_mean"], 3)` (`r round(cov_effect_ranges.table[1, "max_95HDPL"], 3)`, `r round(cov_effect_ranges.table[1, "max_95HDPU"], 3)`), winter flow from `r round(cov_effect_ranges.table[2, "min_mean"], 3)` (`r round(cov_effect_ranges.table[2, "min_95HDPL"], 3)`, `r round(cov_effect_ranges.table[2, "min_95HDPU"], 3)`) to `r round(cov_effect_ranges.table[2, "max_mean"], 3)` (`r round(cov_effect_ranges.table[2, "max_95HDPL"], 3)`, `r round(cov_effect_ranges.table[2, "max_95HDPU"], 3)`), and spring flow from `r round(cov_effect_ranges.table[3, "min_mean"], 3)` (`r round(cov_effect_ranges.table[3, "min_95HDPL"], 3)`, `r round(cov_effect_ranges.table[3, "min_95HDPU"], 3)`) to `r round(cov_effect_ranges.table[3, "max_mean"], 3)` (`r round(cov_effect_ranges.table[3, "max_95HDPL"], 3)`, `r round(cov_effect_ranges.table[3, "max_95HDPU"], 3)`). `r round(pct_effects_negative.table[1,2], 2)`% of segments experienced a significant negative effect of summer temperature (95% HPDI) and `r round(pct_effects_negative.table[2,2], 2)`% of segments experienced a significant negative effect of winter flow. There was no notable spatial structure in covariate effects on YOY brook trout abundance (model $\bf{\beta}_i$s) (Fig. \@ref(fig:YOY-climate-effects-semivariogram-plot)). Neither were model $\bf{\beta}_i$s for YOY geographically correlated (Fig. \@ref(fig:YOY-betas-corrPlot-plot)).

### Synchrony
Estimates of segment-specific ICC values varied from `r round(min(YOY_ICCs.table$mean), 3)` to `r round(max(YOY_ICCs.table$mean), 3)` for YOY brook trout and from `r round(min(Adult_ICCs.table$mean), 3)` to `r round(max(Adult_ICCs.table$mean), 3)` for adult brook trout. YOY brook trout showed moderately higher average synchrony than adult brook trout (`r round(mean(YOY_ICCs.table$mean), 3)` vs. `r round(mean(Adult_ICCs.table$mean), 3)`). On average, northern brook trout populations were more synchronous than southern populations (average YOY ICC: `r round(mean(YOY_ICCs_N.table[,"mean"]), 3)` vs. `r round(mean(YOY_ICCs_S.table[,"mean"]), 3)`), however the three populations with the lowest YOY ICC (<0.01; most asynchronous) were in northern Maryland (Fig.\@ref(fig:YOY-ICC-map)). Several of the most synchronous populations (highest ICC) were in the southern end of North Carolina, near Great Smoky Mountain National Park. There was considerable geographic heterogeneity in spatial synchrony (Fig.\@ref(fig:YOY-ICC-map)), and segment-specific synchrony showed moderate spatial structure (Fig. \@ref(fig:YOY-ICC-semivariogram-plot)), lending support to the idea that populations nearer to each other are more similar than populations farther from each other. 

```{r YOY-ICC-map, fig.cap = "Intraclass correlation coefficient (ICC) values for populations of young-of-year brook trout in the southeastern USA."}
YOY_ICC_map.plot
```

### Climate Effects on Synchrony   
*This section to be revisited after reviewing C-val method with Mevin in January* Spatial synchrony in YOY brook trout density can be partially explained by climate variables, as evidenced by calculations of $C_\epsilon$ (Eq. \@ref(eq:C-eps)). That is, summer temperature and winter and spring flow accounted for `r round(Global_Cs.table[1,3], 3) * 100`% of the synchronous variance in YOY density. Of the three climate covariates, high winter flows explained the most synchronous variance, at `r round(Global_Cs.table[5,3], 3) * 100`%. Spring flow followed with `r round(Global_Cs.table[7,3], 3) * 100`% of synchronous variation explained. The three climate variables did not explain spatial synchrony in adult brook trout density, as all calculations of $C_\epsilon$ for adults were negative. This is because spatial synchrony in adult brook trout density is low to start with and none of the climate variables considered had significant effects on adult brook trout abundance. Climate is acting as a minor synchronizing agent in YOY brook trout populations, however the vast majority of synchronous variation (`r 100 - (round(Global_Cs.table[1,3], 3) * 100)`%) is not explained by these variables. Conversely, climate variables explained even less of the site-specific asynchrony (mean 0%). There were, however, several individual populations for which climate variables explained large amounts of asynchrony. At Wolf Laurel Branch in North Carolina (YOY ICC `r round(YOY_ICCs.table[YOY_ICCs.table$COMID == 19721017, "mean"], 3)`), summer temperature explained `r round(Local_Cs.table[Local_Cs.table$COMID == 19721017, "C_YOY_partialSummTemp"], 3) * 100`% of asynchrony. Climate therefore appears to have a stronger, albeit weak, synchronizing effect on brook trout populations than it does an asynchronizing effect.  