---
title: ''
output: bookdown::pdf_document2
date: "`r Sys.Date()`"
---

## Correlogram Analysis

The average scale and magnitude of spatial synchrony in both YOY and adult brook trout was low compared with those of a suite of climate variables (Fig. \@ref(fig:compound-corrgram-plot)). Correlation lengths measured using the 95% confidence envelope of the spline correlogram were `r round(YOY_corrgram_summary.table$quantiles["0.025", "x"])` km in YOY and `r round(Adult_corrgram_summary.table$quantiles["0.025", "x"])` km in adult brook trout. Point estimates for the scale of synchrony were roughly 100 km for YOY and 200 km for adults. Summer air and water temperature and winter streamflow and precipitation were synchronous to scales of 400 km or more. There was little overlap in the 95% confidence interval (CI) of initial pairwise correlation between trout density and abiotic variables. Average pairwise correlations in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$Regional.synch[1], 2)` and `r round(Adult_corrgram_summary.table$Regional.synch[1], 2)`, respectively, and those of the climate variables ranged from `r round(SummWaterTempObs_corrgram_summary.table$Regional.synch[1], 2)` to `r round(FlowEst_corrgram_summary.table$Regional.synch[1], 2)`. The average magnitude of synchrony was greater in the northern than southern sub-region for both life stages (Fig. \@ref(fig:faceted-corrgram-plot)). Initial pairwise correlation was considerably higher in the northern sub-region for adults (mean = 0.31; 95% CI = 0.16 to 0.46 vs. mean = 0.06; 95% CI = -0.1 to 0.2 for the southern sub-region). The scale of synchrony did not differ greatly between sub-regions.

(ref:compound-corrgram-plot-cap) Spline correlogram of pairwise correlation in brook trout (*Salvelinus fontinalis*) log density  (1995-2015) and selected climate variables for the southeast USA. Climate variables: mean estimated monthly winter (Dec. - Feb.) flow (1980-2015), mean daily observed summer (June - Sep.) air temperature (2010-2015), mean daily observed summer water temperature (2010-2015), and total observed monthly winter precipitation (2008-2013). Shading indicates 95% confidence envelopes. Dashed lines represent average pairwise correlations. Climate data sources: USGS NHDPlus v2.1, USDA Forest Service, NOAA.

```{r compound-corrgram-plot, fig.cap="(ref:compound-corrgram-plot-cap)"}
compound_corrgram2.plot
```

(ref:faceted-corrgram-plot-cap) Spline correlogram of brook trout (*Salvelinus fontinalis*) log density by life stage and sub-region. Shaded regions represent 95% confidence envelope. Dashed lines represent average pairwise correlations.

```{r faceted-corrgram-plot, fig.cap="(ref:faceted-corrgram-plot-cap)"}
compound_corrgram_BKT.plot
```

## Hierarchical Model

Lacking random effects, predictive ability of the climate effect models was modest. Bayesian p-values for mean and coefficient of variation of pass 1 abundance were `r round(PPC_pvals.table[1,4], 2)` and `r round(PPC_pvals.table[2,4], 2)` (YOY) and `r round(PPC_pvals.table[5,4], 2)` and `r round(PPC_pvals.table[6,4], 2)` (adult). Predictive ability of the random effects models improved considerably, with Bayesian p-values for mean and coefficient of variation of pass 1 abundance of `r round(PPC_pvals.table[3,4], 2)` and `r round(PPC_pvals.table[4,4], 2)` (YOY) and `r round(PPC_pvals.table[7,4], 2)` and `r round(PPC_pvals.table[8,4], 2)` (adult). Electrofishing capture probability per pass ($p$) was higher for adults than YOY. Estimates of capture probability varied by agency, with the mean probability ranging from `r round(min(Detect_probs_YOY.table[,"mean"]), 2)` (95% HPDI = `r round(Detect_probs_YOY.table[which.min(Detect_probs_YOY.table$mean),5], 2)` to `r round(Detect_probs_YOY.table[which.min(Detect_probs_YOY.table$mean),6], 2)`) to `r round(max(Detect_probs_YOY.table[,"mean"]), 2)` (95% HPDI = `r round(Detect_probs_YOY.table[which.max(Detect_probs_YOY.table$mean),5], 2)` to `r round(Detect_probs_YOY.table[which.max(Detect_probs_YOY.table$mean),6], 2)`) for YOY and from `r round(min(Detect_probs_Adult.table[,"mean"]), 2)` (95% HPDI = `r round(Detect_probs_Adult.table[which.min(Detect_probs_Adult.table$mean),5], 2)` to `r round(Detect_probs_Adult.table[which.min(Detect_probs_Adult.table$mean),6], 2)`) to `r round(max(Detect_probs_Adult.table[,"mean"]), 2)` (95% HPDI = `r round(Detect_probs_Adult.table[which.max(Detect_probs_Adult.table$mean),5], 2)` to `r round(Detect_probs_Adult.table[which.max(Detect_probs_Adult.table$mean),6], 2)`) for adults (Fig. \@ref(fig:detect-probs)).

### Overall Climate Effects Across Stream Segments

Climate effects on brook trout abundance varied by life stage, as represented by posterior distributions of the mean parameters for $\bm{\mu}_\beta$ (Fig. \@ref(fig:cov-effects-plot)). As predicted, YOY were more affected by climate than were adults, thus unless noted otherwise we focus here on YOY responses. At the regional scale (Fig. \@ref(fig:cov-effects-plot)), all three environmental covariates had negative effects on YOY abundance, while summer air temperature and winter flow had negative effects on adult abundance. Winter high flow had the strongest negative effect on YOY abundance (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", 5], 2)`), closely followed by spring high flow (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", 5], 2)`) and high temperatures in the previous summer (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`).

(ref:cov-effects-plot-cap) 95% highest posterior density intervals (HDPIs) for climate effects on brook trout (*Salvelinus fontinalis*) log density by life stage and sub-region. Climate variables: average 0.9Q summer air temperature (year t-1), max 0.9Q winter stream flow (year t), max 0.9Q spring stream flow (year t). Data sources: USGS NHDPlus v2.1, NOAA.

```{r cov-effects-plot, fig.cap = "(ref:cov-effects-plot-cap)"}
cov_effects.plot
```

Covariate effects also varied by sub-region. As hypothesized, summer air temperature had a stronger effect on YOY in the south than in the north (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)` vs. mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`). In the northern sub-region (symbolized in green in Fig. \@ref(fig:cov-effects-plot)), YOY abundance was predominantly driven by flow (winter flow mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", "mean"], 2)` and 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", 5], 2)` and spring flow mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", "mean"], 2)` and 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", 5], 2)`), with no significant effect of summer air temperature (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`). In the southern sub-region (symbolized in orange in Fig. \@ref(fig:cov-effects-plot)), YOY abundance was primarily driven by summer air temperature (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`). A negative effect of summer air temperature on adult abundance (mean = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", 5], 2)`) was detected in both sub-regions. Overall, stream flows were the primary driver of YOY abundance over time in the northern sub-region, whereas summer air temperature was the most important driver of YOY abundance in the southern sub-region.

### Spatial Heterogeneity in Climate Effects

Climate effects varied considerably among stream segments, a sign of local cross-scale interactions (Fig. \@ref(fig:YOY-climate-effects-map)). The variance in local effects ($\bm{\sigma}^2_\beta$) for winter stream flow on YOY abundance (mean = `r round(cov_effect_variances.table[2,"mean"], 2)`; 95% HPDI = `r round(cov_effect_variances.table[2,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[2,"X95._HPDU"], 2)`) was smaller than that of spring stream flow (mean = `r round(cov_effect_variances.table[3,"mean"], 2)`; 95% HPDI = `r round(cov_effect_variances.table[3,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[3,"X95._HPDU"], 2)`) or summer temperature (mean = `r round(cov_effect_variances.table[1,"mean"], 2)`; 95% HPDI = `r round(cov_effect_variances.table[1,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[1,"X95._HPDU"], 2)`; Fig. \@ref(fig:YOY-climate-effects-map)). These results showed that winter stream flow had the most spatially homogeneous effect on YOY abundance. Variances in local climate effects on adult abundance were comparable, and 95% HPDIs overlapped (summer temperature variance: `r round(cov_effect_variances.table[4,"mean"], 2)` (95% HPDI = `r round(cov_effect_variances.table[4,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[4,"X95._HPDU"], 2)`), winter stream flow variance: `r round(cov_effect_variances.table[5,"mean"], 2)` (95% HPDI = `r round(cov_effect_variances.table[5,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[5,"X95._HPDU"], 2)`), spring stream flow variance: `r round(cov_effect_variances.table[6,"mean"], 2)` (95% HPDI = `r round(cov_effect_variances.table[6,"X95._HPDL"], 2)` to `r round(cov_effect_variances.table[6,"X95._HPDU"], 2)`)). Correlation analysis demonstrated that there was little influence of local habitat (e.g. land cover, elevation, channel slope, watershed area) on segment-specific responses to climate ($\bm{\beta_i}$; Table \@ref(tab:YOY-betas-corr-table)). There was also little spatial structure in covariate effects on YOY brook trout abundance (segment-specific $\bm{\beta_i}$, Fig. \@ref(fig:YOY-climate-effects-semivariogram-plot)).

(ref:YOY-climate-effects-map-cap) Local climate effects on brook trout (*Salvelinus fontinalis*) young-of-the-year abundance (model $\bm{\beta}_i$). a) average 0.9Q summer air temperature (year t-1), b) max 0.9Q winter stream flow (year t), and c) max 0.9Q spring stream flow (year t). Data sources: USGS NHDPlus v2.1, NOAA.

```{r YOY-climate-effects-map, fig.cap="(ref:YOY-climate-effects-map-cap)", fig.height = 8}
plot_grid(YOY_SummTemp_betas.plot,
          YOY_WintFlow_betas.plot,
          YOY_SprFlow_betas.plot,
          labels = c("a) Summer Temperature", "b) Winter Flow", "c) Spring Flow"),
          label_size = 11,
          nrow = 3)
```

### Synchrony

Estimates of segment-specific ICC values varied from `r round(min(YOY_ICCs.table$mean), 2)` (95% HPDI = `r round(YOY_ICCs.table[which.min(YOY_ICCs.table$mean), 4], 3)` to `r round(YOY_ICCs.table[which.min(YOY_ICCs.table$mean), 5], 2)`) to `r round(max(YOY_ICCs.table$mean), 2)` (95% HPDI = `r round(YOY_ICCs.table[which.max(YOY_ICCs.table$mean), 4], 2)` to `r round(YOY_ICCs.table[which.max(YOY_ICCs.table$mean), 5], 2)`) for YOY brook trout and from `r round(min(Adult_ICCs.table$mean), 4)` (95% HPDI = `r round(Adult_ICCs.table[which.min(Adult_ICCs.table$mean), 4], 5)` to `r round(Adult_ICCs.table[which.min(Adult_ICCs.table$mean), 5], 3)`) to `r round(max(Adult_ICCs.table$mean), 2)` (95% HPDI = `r round(Adult_ICCs.table[which.max(Adult_ICCs.table$mean), 4], 2)` to `r round(Adult_ICCs.table[which.max(Adult_ICCs.table$mean), 5], 2)`) for adult brook trout. YOY brook trout showed higher average ICC than adult brook trout (`r round(mean(YOY_ICCs.table$mean), 2)` vs. `r round(mean(Adult_ICCs.table$mean), 2)`), showing that YOY abundance is more synchronous across populations than adult abundance. On average, northern brook trout populations were more synchronous than southern populations (average YOY ICC: `r round(mean(YOY_ICCs_N.table[,"mean"]), 2)` vs. `r round(mean(YOY_ICCs_S.table[,"mean"]), 2)`), which conforms with findings from the spline correlograms above. However, several of the most synchronous populations (highest YOY ICC) were in southern sub-region (Fig. \@ref(fig:YOY-ICC-map), but see Fig. \@ref(fig:Adult-ICC-map) for adult ICCs). There was only moderate correlation between ICC and local habitat variables (Table \@ref(tab:YOY-ICCs-corr-table)). There was considerable geographic heterogeneity in spatial synchrony (Fig. \@ref(fig:YOY-ICC-map)), and segment-specific synchrony showed moderate spatial structure (Fig. \@ref(fig:YOY-ICC-semivariogram-plot)), showing that populations nearer to each other are more similar in temporal abundance patterns than populations farther from each other. Variability in average abundance across all stream segments was lower than in individual segments (Fig. \@ref(fig:CVs-plot)), indicating a portfolio effect among the sampled populations. The coefficient of variation for interannual observed pass 1 abundance for YOY brook trout averaged across segments was `r round(CVs.table[145,1], 2)`, compared to a mean of `r round(mean(CVs.table[1:144,1], na.rm = T), 2)` for individual segments.

(ref:YOY-ICC-map-cap) Intraclass correlation coefficient (ICC) values for young-of-the-year brook trout abundance in the southeastern USA. High ICC values indicate synchrony relative to the temporal variation averaged across segments, while low ICC values indicate asynchrony. The five stream segments with lowest ICC (least synchronous) are indicated by "+".

```{r YOY-ICC-map, fig.cap = "(ref:YOY-ICC-map-cap)"}
YOY_ICC_map.plot
```