---
title: ''
output: bookdown::pdf_document2
date: "`r Sys.Date()`"
---

## Correlogram Analysis

The average scale and magnitude of spatial synchrony in both YOY and adult brook trout was relatively low compared with those of a suite of climate variables (Fig. \@ref(fig:compound-corrgram-plot)). The 95% CI of initial pairwise correlation did not overlap between trout density and abiotic variables. Correlation lengths measured using the 2.5$^{th}$ percentile of the 95% confidence envelope of the spline correlogram were `r round(YOY_corrgram_summary.table$quantiles["0.025", "x"])` km in YOY and `r round(Adult_corrgram_summary.table$quantiles["0.025", "x"])` km in adult brook trout. Point estimates for the scale of synchrony were roughly 150 km for both life stages. Summer air and water temperature and winter streamflow and precipitation were synchronous to scales of 400 km or more. Average pairwise correlations in YOY and adult brook trout were `r round(YOY_corrgram_summary.table$Regional.synch[1], 2)` and `r round(Adult_corrgram_summary.table$Regional.synch[1], 2)`, respectively, and those of the climate variables ranged from `r round(SummWaterTempObs_corrgram_summary.table$Regional.synch[1], 2)` to `r round(FlowEst_corrgram_summary.table$Regional.synch[1], 2)`. Initial pairwise correlation was considerably higher in the northern sub-region for adults (mean = 0.29; 95% CI = 0.14 to 0.47 vs. mean = 0.07; 95% CI = -0.08 to 0.2 for the southern sub-region). However, neither the scale nor average magnitude of synchrony differed greatly between sub-regions (Fig. \@ref(fig:faceted-corrgram-plot)).

(ref:compound-corrgram-plot-cap) Spline correlogram of pairwise correlation in brook trout (*Salvelinus fontinalis*) density and selected climate variables for the southeast USA. Climate variables: mean estimated monthly winter flow, mean daily observed summer air temperature, mean daily observed summer water temperature, and total observed monthly winter precipitation. Brook trout density is log transformed. Shading indicates 95% confidence envelopes. Dashed lines represent average pairwise correlations. Climate data sources: USGS NHDPlus v2.1, USDA Forest Service, NOAA.

```{r compound-corrgram-plot, fig.cap="(ref:compound-corrgram-plot-cap)"}
compound_corrgram2.plot
```

(ref:faceted-corrgram-plot-cap) Spline correlogram of log brook trout (*Salvelinus fontinalis*) density by life stage and sub-region. Shaded regions represent 95% confidence envelope. Dashed lines represent average pairwise correlations.

```{r faceted-corrgram-plot, fig.cap="(ref:faceted-corrgram-plot-cap)"}
compound_corrgram_BKT.plot
```

## Hierarchical Model

Lacking random effects, predictive ability of the climate effect models was modest. Bayesian p-values for mean and coefficient of variation of pass 1 abundance were `r round(PPC_pvals.table[1,4], 2)` and `r round(PPC_pvals.table[2,4], 2)` (YOY) and `r round(PPC_pvals.table[5,4], 2)` and `r round(PPC_pvals.table[6,4], 2)` (adult). Predictive ability of the random effects models was improved considerably because these models accounted for temporal and spatiotemporal variability. Bayesian p-values for mean and coefficient of variation of pass 1 abundance were `r round(PPC_pvals.table[3,4], 2)` and `r round(PPC_pvals.table[4,4], 2)` (YOY) and `r round(PPC_pvals.table[7,4], 2)` and `r round(PPC_pvals.table[8,4], 2)` (adult). Electrofishing capture probability per pass ($p$) was higher for adults than YOY. Estimates of capture probability varied by data source, with the mean probability ranging from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` (95% HPDI = `r round(Detect_probs.table[5,5], 2)` to `r round(Detect_probs.table[5,6], 2)`) to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "YOY", "mean"]), 2)` (95% HPDI = `r round(Detect_probs.table[8,5], 2)` to `r round(Detect_probs.table[8,6], 2)`) for YOY and from `r round(min(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` (95% HPDI = `r round(Detect_probs.table[16,5], 2)` to `r round(Detect_probs.table[16,6], 2)`) to `r round(max(Detect_probs.table[Detect_probs.table$Life_Stage == "Adult", "mean"]), 2)` (95% HPDI = `r round(Detect_probs.table[17,5], 2)` to `r round(Detect_probs.table[17,6], 2)`) for adults (Fig. \@ref(fig:detect-probs)).

### Overall Climate Effects Across Stream Segments

Climate effects on brook trout abundance varied by sub-region and life stage, as represented by posterior distributions of the mean parameters for $\bm{\mu}_\beta$ (Fig. \@ref(fig:cov-effects-plot)). In all cases, YOY were more affected by climate than were adults, thus unless noted otherwise we focus here on YOY responses. At the regional scale (symbolized in green in Fig. \@ref(fig:cov-effects-plot)), all three environmental covariates had negative effects on YOY abundance, while only summer air temperature had an effect on adult abundance. Winter high flow had the strongest negative effect on YOY abundance (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "WintFlow", 5], 2)`), followed by spring high flow (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SprFlow", 5], 2)`) and high temperatures in the previous summer (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "All" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`).

(ref:cov-effects-plot-cap) Full posterior distributions for climate effects on brook trout (*Salvelinus fontinalis*) log density by life stage and sub-region. Climate variables: average 0.9Q summer air temperature (year t-1), max 0.9Q winter stream flow (year t), max 0.9Q spring stream flow (year t). Data sources: USGS NHDPlus v2.1, NOAA.

```{r cov-effects-plot, fig.cap = "(ref:cov-effects-plot-cap)"}
cov_effects.plot
```

Covariate effects at the sub-regional scale varied. As hypothesized, air temperature had a stronger effect on YOY in the south than in the north (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)` vs. mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`). Within the northern sub-region (symbolized in orange in Fig. \@ref(fig:cov-effects-plot)), YOY abundance was exclusively driven by flow (winter flow mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", "mean"], 2)` and 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "WintFlow", 5], 2)` and spring flow mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", "mean"], 2)` and 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SprFlow", 5], 2)`), with no effect of summer air temperature (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "North" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)`). Within the southern sub-region (symbolized in purple in Fig. \@ref(fig:cov-effects-plot)), summer air temperature and winter flow had the strongest negative effect on YOY abundance (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SummTemp", 5], 2)` and mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "WintFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "WintFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "WintFlow", 5], 2)`). The effect of spring flows on YOY density in the south trended positive (mean = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SprFlow", "mean"], 2)`; 95% HPDI = `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SprFlow", 4], 2)` to `r round(YOY_mu.betas.table[YOY_mu.betas.table$subregion == "South" & YOY_mu.betas.table$covar == "SprFlow", 5], 2)`). A slight overall negative effect of summer air temperature on adult abundance (mean = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "All" & Adult_mu.betas.table$covar == "SummTemp", 5], 2)`) was driven by the response of northern populations (mean = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "North" & Adult_mu.betas.table$covar == "SummTemp", "mean"], 2)`; 95% HPDI = `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "North" & Adult_mu.betas.table$covar == "SummTemp", 4], 2)` to `r round(Adult_mu.betas.table[Adult_mu.betas.table$subregion == "North" & Adult_mu.betas.table$covar == "SummTemp", 5], 2)`). Uncertainty in climate effects on adults in southern populations was much greater than that of northern populations (Fig. \@ref(fig:cov-effects-plot)). Overall, winter and spring stream flows were the primary driver of YOY abundance over time in the northern sub-region, whereas summer air temperature and winter stream flow were the most important drivers of YOY abundance in the southern sub-region.

### Spatial Heterogeneity in Climate Effects

Climate effects varied considerably among stream segments (Fig. \@ref(fig:YOY-climate-effects-map)). With this cross-scale interaction, some experienced positive effects, while others experienced negative effects. The variance in local effects ($\bm{\sigma}^2_\beta$) for winter stream flow on YOY abundance (mean = `r round(cov_effect_variances.table[2,"mean"], 1)`; 95% HPDI = `r round(cov_effect_variances.table[2,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[2,"X95._HPDU"], 1)`) was smaller than that of spring stream flow (mean = `r round(cov_effect_variances.table[3,"mean"], 1)`; 95% HPDI = `r round(cov_effect_variances.table[3,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[3,"X95._HPDU"], 1)`) or summer temperature (mean = `r round(cov_effect_variances.table[1,"mean"], 1)`; 95% HPDI = `r round(cov_effect_variances.table[1,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[1,"X95._HPDU"], 1)`; Fig. \@ref(fig:YOY-climate-effects-map)). Summer temperature had the smallest variance in local effects on adult abundance (mean = `r round(cov_effect_variances.table[4,"mean"], 1)` (95% HPDI = `r round(cov_effect_variances.table[4,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[4,"X95._HPDU"], 1)`), compared to `r round(cov_effect_variances.table[5,"mean"], 1)` (95% HPDI = `r round(cov_effect_variances.table[5,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[5,"X95._HPDU"], 1)`) for winter stream flow and `r round(cov_effect_variances.table[6,"mean"], 1)` (95% HPDI = `r round(cov_effect_variances.table[6,"X95._HPDL"], 1)` to `r round(cov_effect_variances.table[6,"X95._HPDU"], 1)`) for spring stream flow). Mean variance in climate effects on YOY was higher than that of adults (mean = `r round(mean(cov_effect_variances.table[1:3,"mean"]), 1)` vs. `r round(mean(cov_effect_variances.table[4:6,"mean"]), 1)`). Correlation analysis demonstrated that there was little influence of local habitat on model $\bm{\beta_i}$ (Table \@ref(tab:YOY-betas-corr-table)). There was no notable spatial structure in covariate effects on YOY brook trout abundance (model $\bm{\beta_i}$, Fig. \@ref(fig:YOY-climate-effects-semivariogram-plot)).

(ref:YOY-climate-effects-map-cap) Local climate effects on brook trout (*Salvelinus fontinalis*) young-of-the-year abundance (model $\bm{\beta}_i$). a) average 0.9Q summer air temperature (year t-1), b) max 0.9Q winter stream flow (year t), and c) max 0.9Q spring stream flow (year t). Data sources: USGS NHDPlus v2.1, NOAA.

```{r YOY-climate-effects-map, fig.cap="(ref:YOY-climate-effects-map-cap)", fig.height = 8}
plot_grid(YOY_SummTemp_betas.plot,
          YOY_WintFlow_betas.plot,
          YOY_SprFlow_betas.plot,
          labels = c("a)", "b)", "c)"),
          label_size = 11,
          nrow = 3)
```

### Synchrony

Estimates of segment-specific ICC values varied from `r round(min(YOY_ICCs.table$mean), 2)` (95% HPDI = `r round(YOY_ICCs.table[which.min(YOY_ICCs.table$mean), 4], 2)` to `r round(YOY_ICCs.table[which.min(YOY_ICCs.table$mean), 5], 2)`) to `r round(max(YOY_ICCs.table$mean), 2)` (95% HPDI = `r round(YOY_ICCs.table[which.max(YOY_ICCs.table$mean), 4], 2)` to `r round(YOY_ICCs.table[which.max(YOY_ICCs.table$mean), 5], 2)`) for YOY brook trout and from `r round(min(Adult_ICCs.table$mean), 2)` (95% HPDI = `r round(Adult_ICCs.table[which.min(Adult_ICCs.table$mean), 4], 2)` to `r round(Adult_ICCs.table[which.min(Adult_ICCs.table$mean), 5], 2)`) to `r round(max(Adult_ICCs.table$mean), 2)` (95% HPDI = `r round(Adult_ICCs.table[which.max(Adult_ICCs.table$mean), 4], 2)` to `r round(Adult_ICCs.table[which.max(Adult_ICCs.table$mean), 5], 2)`) for adult brook trout. YOY brook trout showed higher average ICC than adult brook trout (`r round(mean(YOY_ICCs.table$mean), 2)` vs. `r round(mean(Adult_ICCs.table$mean), 2)`). On average, northern brook trout populations were more synchronous than southern populations (average YOY ICC: `r round(mean(YOY_ICCs_N.table[,"mean"]), 2)` vs. `r round(mean(YOY_ICCs_S.table[,"mean"]), 2)`). There was little correlation between ICC and local habitat variables (Table \@ref(tab:YOY-ICCs-corr-table)). Several of the most synchronous populations (highest YOY ICC) were in northeast of the study region (Fig. \@ref(fig:YOY-ICC-map), but see Fig. \@ref(fig:Adult-ICC-map) for adult ICCs). There was considerable geographic heterogeneity in spatial synchrony (Fig. \@ref(fig:YOY-ICC-map)), and segment-specific synchrony showed moderate spatial structure (Fig. \@ref(fig:YOY-ICC-semivariogram-plot)), showing that populations nearer to each other are more similar in temporal abundance patterns than populations farther from each other. Variability in average abundance across all stream segments was lower than in individual segments (Fig. \@ref(fig:CVs-plot)), indicating the presence of a portfolio effect among the sampled populations. The coefficient of variation for interannual observed pass 1 abundance for YOY brook trout averaged across segments was `r round(CVs.table[171,1], 2)`, compared to a mean of `r round(mean(CVs.table[1:170,1], na.rm = T), 2)` for individual segments.

(ref:YOY-ICC-map-cap) Intraclass correlation coefficient (ICC) values for populations of young-of-the-year brook trout (*Salvelinus fontinalis*) in the southeastern USA. High ICC values indicate synchrony relative to the temporal variation averaged across segments, while low ICC values indicate asynchrony. The five stream segments with lowest ICC (least synchronous) are indicated by "+".

```{r YOY-ICC-map, fig.cap = "(ref:YOY-ICC-map-cap)"}
YOY_ICC_map.plot
```